---
title: "Saving track information"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Saving track information}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setupvignette, include = FALSE}
library(here)
if (file.exists(here("_not_included", "myenviron.R"))) {
  source(here("_not_included", "myenviron.R"))
}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(openmusesampling)
library(spotifyr)
library(knitr)
## A relatively compless track item:
start_time <- xsd_time()
start_time
one_track <- spotifyr::get_track("14ngWWxvUSnIMXgF6rzSk1")
```

```{r extract-isrc}
extract_isrc(one_track)
```

We will need to connect tracks and artists, but often, one track is connected to a list of artists. To store it effectively in a data.frame, we will concatenate the list artist identifiers into a single character string.

```{r extract-artist-uri}
extract_artist_uri(one_track)
```

Only a few characteristics of the song change over time. We record these separately, because they need to be saved each time we "see" the same track. However, its constants do not need to be re-saved all the time.

```{r extract_temporal_variables}
extract_track_variables(track_df = one_track, time_query = start_time )
```

### Variables to keep

There is some returned information that is time-sensitive.  The popularity of the track or the number of markets changes over time.

```{r}
get_track_vars <-tibble::tribble(
  ~spotify_name,        ~name,    ~description, 
  "id",                 "spotify_track_id",   "key column for tracks",
  NA_character_,        "time_query",        "time of query in XSD format",
  "popularity",         "spotify_popularity", "the popularity of the item at the query time.", 
  "available_markets",  "spotify_available_markets", "a concatenated string of markets at query time."
)

knitr::kable(get_track_vars)
```


An attribute is time-invariant information. We can extract a few of them.

```{r extract_variables}
extract_track_attributes(track_df = one_track)
```

### Attributes to keep

The attributes are not changing over time, or changing only due to corrections of clerical errors. In this case, we only need to keep the information, if it is not yet saved. We will create a register of tracks where we already have the attributes, in their case, we only need to keep the variables.

_Please continue with the data that you want to keep. I think that all data should be kept once, i.e., the spotify track id should be kept once, not in URL, URI and ID format._

Could the saved on the attributes table as well and used as a key on the data base?

_Please consider_ `data-raw/get_track_data_raw` _and_ `data/get_track.data.raw` _(which can be reviewed in the package website.) or with_ `?get_track_return_raw`.

- You should first define in each case what do you keep and how:

These could be some of the attributes to keep. Obviously, we need to discuss what we want to keep and if the attributes described below are really useful or not.

```{r get_track_vars}
get_track_vars <-tibble::tribble(
  ~spotify_name,        ~name,                ~description,
  "external_ids.isrc",  "isrc",               "track isrc.",
  "id",                 "spotify_track_id",   "key column for tracks.",
  "name",               "name",               "the name of the track on spotify",
  "duration_ms",        "duration_ms",        "the duration of the recording in ms.", 
  "album.name",         "album_name",         "the name of the album.",
  "album.uri",          "album_uri",          "spotify album's uri.",
  "album.release_date", "release_date",       "the release date of the album.",
  "artist.name",        "artist",             "the name of the artists on spotify.",
  "artist.uri",         "artist_uri",         "spotify artists' uris."
)

knitr::kable(get_track_vars)
```


- Then create in the data-raw/ folder an example of saving the data in the form you want to keep them in store, i.e, a data-raw/mydataset.R

- Then create the sample dataset with `usethis::use_data(get_track_return_raw, overwrite = TRUE)`.  This will attach an example of the dataset to this package.

- Then create the documentation of the dataset using the sample of `R/data_get_track_return_raw.R`, this is how you attach a dataset documentation to an R package.
