---
title: "Saving track information"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Saving track information}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setupvignette, include = FALSE}
library(here)
if (file.exists(here("_not_included", "myenviron.R"))) {
  source(here("_not_included", "myenviron.R"))
}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(openmusesampling)
library(spotifyr)
## A relatively compless track item:
start_time <- xsd_time()
start_time
one_track <- spotifyr::get_track("14ngWWxvUSnIMXgF6rzSk1")
```

```{r extract-isrc}
extract_isrc(one_track)
```

We will need to connect tracks and artists, but often, one track is connected to a list of artists. To store it effectively in a data.frame, we will concatenate the list artist identifiers into a single character string.

```{r extract-artist-uri}
extract_artist_uri(one_track)
```
Only a few characteristics of the song change over time. We record these separately, because they need to be saved each time we "see" the same track. However, its constants do not need to be re-saved all the time.

```{r extract_variables}
extract_track_variables(track_df = one_track, time_query = start_time )
```

