---
title: "search_track_by_term"
author: "Fabio Vieira"
date: "2024-09-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The function

The function search_track_by_terms is supposed to search Spotify API for tracks that contain the term being search. The function only takes on two parameters

- **search_term**: a string containing the term being search (ex: "Olho")
- **wasAssociatedWith**: the ORCID of the person performing the query.

## Example

# Loading packages

```{r}
library(here)
library(spotifyr)
library(openmusesampling)
if (file.exists(here("_not_included", "myenviron.R"))) {
  source(here("_not_included", "myenviron.R"))
}
```

Running a query (this might take several minutes to run)

```{r}
df <- search_tracks_by_term(search_term = "Olho",
                            wasAssociatedWith = "https://orcid.org/0000-0003-4253-1953")
```

## Output

Checking the results

```{r}
head(df)
```

Additional information about the query (i.e. who perform the query, at what time, and so on)

```{r}
attr(df, "prov")
```
